06-assessing_lime_explanations

### 2019-02-11 journals/06-assessing_lime_explanations.Rmd
finished cleaning journals

```{r fig.height = 8, fig.width = 8}
# Plots the top feature for each case for each bin situation
p <- ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")

@@

```{r fig.height = 8, fig.width = 10, eval = FALSE}
hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")

hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(2) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")

hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(3) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")
```

>>>>

```{r fig.height = 8, fig.width = 8}
# Plots the top feature for each case for each bin situation
ggplot(chosen_features, aes(x = situation, y = case, fill = first)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Bin Type", y = "Case", fill = "Feature", title = "First Feature")

@@

```{r fig.height = 12, fig.width = 10}
hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case, feature) %>%
  mutate(order = rep(rep(1:length(levels(factor(case))), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 4, scales = "free_y") +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")

hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(2) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case, feature) %>%
  mutate(order = rep(rep(1:length(levels(factor(case))), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 4, scales = "free_y") +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")

hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(3) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case, feature) %>%
  mutate(order = rep(rep(1:length(levels(factor(case))), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 4, scales = "free_y") +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")
```
